A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Fix typo in V

The R Project is a tool for data analysis.  At its heart is a {vectorized,
  dynamic, lazy, functional, object-oriented} programming language with an
unusual combination of features~\cite{ecoop12} designed to ease learning by
non-programmer and enable rapid development of statistical
methods~\cite{R96}.  The language was designed as a successor to
S~\cite{S88}.

@@

The pipeline begins with downloading and installing open source R packages
from CRAN for the corpus along with their dependencies. The Kaggle programs
are downloaded from \href{http://www.kaggle.com}{Kaggle} separately by a
crawler.  Next, code size and coverage metrics from the installed packages
are extracted using the \href{ https://github.com/r-lib/covr}{\covr}
package. This is followed by extraction of runnable programs from R
packages: tests, examples and vignettes as well as from Kaggle. The code of
each extracted program is wrapped into a call to dynamic analyzer
\emph{evil} (\emph{Ev}al \emph{I}nspection \emph{L}ibrary) that collect eval
usage. The reason for this is that we only want to record eval usage for the
extracted code. Without this, the data would include eval calls from the
unit testing frameworks as well as from bootstrapping R virtual machine
itself. To avoid any interference, each program is run in its own R
instance. The \emph{evil} framework implemented as R package in 2K lines of
R and 400 lines of C++ code.

@@

To represent end-user code in the corpus, we turned to
Kaggle,\footnote{\url{https://www.kaggle.com}} an online platform for
data-science and machine-learning. The website allow people to share
data-science competitions, a data-analysis problem together with data, for
which users try to find the best solution. The solutions, called {kernels},
are then shared back to the platform in the form of either plain scripts or
as notebooks.  One of the most popular competition is about predicting
passenger survival on
Titanic\footnote{\url{https://www.kaggle.com/c/titanic}} with \CorpusKaggle
kernels in R (over 1/4 of all available R kernels) which we used for our
corpus.

>>>>

The R Project is a tool for data analysis.  At its heart it is a {vectorized,
  dynamic, lazy, functional, object-oriented} programming language with an
unusual combination of features~\cite{ecoop12} designed to ease learning by
non-programmer and enable rapid development of statistical
methods~\cite{R96}.  The language was designed as a successor to
S~\cite{S88}.

@@

The pipeline begins with downloading and installing open source R packages
from CRAN for the corpus along with their dependencies. The Kaggle programs
are downloaded from \href{http://www.kaggle.com}{Kaggle} separately by a
crawler.  Next, code size and coverage metrics from the installed packages
are extracted using the \href{ https://github.com/r-lib/covr}{\covr}
package. This is followed by extraction of runnable programs from R
packages: tests, examples and vignettes as well as from Kaggle. The code of
each extracted program is wrapped into a call to dynamic analyzer
\emph{evil} (\emph{Ev}al \emph{I}nspection \emph{L}ibrary) that collects eval
usage. The reason for this is that we only want to record eval usage for the
extracted code. Without this, the data would include eval calls from the
unit testing frameworks as well as from bootstrapping R virtual machine
itself. To avoid any interference, each program is run in its own R
instance. The \emph{evil} framework implemented as R package in 2K lines of
R and 400 lines of C++ code.

@@

To represent end-user code in the corpus, we turned to
Kaggle,\footnote{\url{https://www.kaggle.com}} an online platform for
data-science and machine-learning. The website allows people to share
data-science competitions, a data-analysis problem together with data, for
which users try to find the best solution. The solutions, called {kernels},
are then shared back to the platform in the form of either plain scripts or
as notebooks.  One of the most popular competition is about predicting
passenger survival on
Titanic\footnote{\url{https://www.kaggle.com/c/titanic}} with \CorpusKaggle
kernels in R (over 1/4 of all available R kernels) which we used for our
corpus.
